---
title: "Stats - Slime mold"
author: "AMARA Y., DESPEYROUX T., SCHWARZ S."
date: "05/12/2021"
output: html_document
---


# Libraries importation

```{r library, include=FALSE}
library(ggplot2)
library(cowplot)
library(dplyr)
library("gridExtra")
library(tidyverse)
```

# Data importation

```{r, echo=FALSE}
#Put you working directory : setwd(" ")

PC<-read.table("path_chosen.csv", header = TRUE, dec=",", sep=";")
GR<-read.table("growth_rate.csv", header = TRUE, dec=",", sep=";")

GR$Check.time <- as.character(GR$Check.time)
GR$Time.of.training  <- as.character(GR$Time.of.training)
PC$Check.time <- as.character(PC$Check.time)
PC$Time.of.training  <- as.character(PC$Time.of.training)

GR_9<- GR %>%
  filter(Check.time==9) %>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type)) 

GR_49<- GR %>%
  filter(Check.time==49) %>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type)) 

GR_control<- GR %>%
  filter(Medium.Type=="Control +") %>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type)) %>% 
  mutate(Check.time = ifelse(Check.time == "49", "2.49", Check.time)) %>% 
    mutate(Check.time = ifelse(Check.time == "9", "1.9", Check.time))
  

GR_insecticide<- GR %>%
  filter(Medium.Type=="Test") %>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type)) %>% 
  mutate(Check.time = ifelse(Check.time == "49", "2.49", Check.time)) %>% 
    mutate(Check.time = ifelse(Check.time == "9", "1.9", Check.time))


PC_test_1<- PC %>% 
  filter(Medium.Type=="Test" & Check.time==4)%>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type)) %>% 
  mutate(PC.Direction = ifelse(Individual == "2", "No growth", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(Individual == "3", "No growth", PC.Direction)) %>%
  mutate(PC.Direction = ifelse(Individual == "4", "No growth", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "no choice", "No choice", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "non chemical", "Without insecticide", PC.Direction))


PC_test_2<- PC %>% 
  filter(Medium.Type=="Test" & Check.time==8.5)%>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type))%>% 
  mutate(PC.Direction = ifelse(Individual == "2", "No growth", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(Individual == "3", "No growth", PC.Direction)) %>%
  mutate(PC.Direction = ifelse(Individual == "4", "No growth", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "no choice", "No choice", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "non chemical", "Without insecticide", PC.Direction))

PC_test_3<- PC %>% 
  filter(Medium.Type=="Test" & Check.time==23.5)%>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type))%>% 
  mutate(PC.Direction = ifelse(PC.Direction == "no choice", "No choice", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "non chemical", "Without insecticide", PC.Direction))

PC_test_4<- PC %>% 
  filter(Medium.Type=="Test" & Check.time==97)%>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type))%>% 
  mutate(PC.Direction = ifelse(PC.Direction == "no choice", "No choice", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "non chemical", "Without insecticide", PC.Direction))


PC_controlpos_1<-PC %>% 
  filter(Medium.Type=="Control +"& Check.time==4)%>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type))%>% 
  mutate(PC.Direction = ifelse(Individual == "5", "No growth", PC.Direction))%>% 
  mutate(PC.Direction = ifelse(PC.Direction == "no choice", "No choice", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "non chemical", "Without insecticide", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "right", "Right", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "left", "Left", PC.Direction))

PC_controlpos_2<-PC %>% 
  filter(Medium.Type=="Control +"& Check.time==8.5)%>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type))%>% 
  mutate(PC.Direction = ifelse(PC.Direction == "no choice", "No choice", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "non chemical", "Without insecticide", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "right", "Right", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "left", "Left", PC.Direction))

PC_controlpos_3<-PC %>% 
  filter(Medium.Type=="Control +"& Check.time==23.5)%>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type))%>% 
  mutate(PC.Direction = ifelse(PC.Direction == "no choice", "No choice", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "non chemical", "Without insecticide", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "right", "Right", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "left", "Left", PC.Direction))

PC_controlpos_4<-PC %>% 
  filter(Medium.Type=="Control +"& Check.time==97)%>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type))%>% 
  mutate(PC.Direction = ifelse(PC.Direction == "no choice", "No choice", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "non chemical", "Without insecticide", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "right", "Right", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "left", "Left", PC.Direction))


PC_controlneg_1<-PC %>% 
  filter(Medium.Type=="Control -"& Check.time==4)%>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type))%>% 
  mutate(PC.Direction = ifelse(Individual == "1", "No growth", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(Individual == "2", "No growth", PC.Direction)) %>%
  mutate(PC.Direction = ifelse(Individual == "3", "No growth", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(Individual == "5", "No growth", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(Individual == "6", "No growth", PC.Direction))%>% 
  mutate(PC.Direction = ifelse(PC.Direction == "no choice", "No choice", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "non chemical", "Without insecticide", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "right", "Right", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "left", "Left", PC.Direction))

PC_controlneg_2<-PC %>% 
  filter(Medium.Type=="Control -"& Check.time==8.5)%>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type))%>% 
  mutate(PC.Direction = ifelse(Individual == "6", "No growth", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "no choice", "No choice", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "non chemical", "Without insecticide", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "right", "Right", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "left", "Left", PC.Direction))

PC_controlneg_3<-PC %>% 
  filter(Medium.Type=="Control -"& Check.time==23.5)%>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type))%>% 
  mutate(PC.Direction = ifelse(Individual == "6", "No growth", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "no choice", "No choice", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "non chemical", "Without insecticide", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "right", "Right", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "left", "Left", PC.Direction))

PC_controlneg_4<-PC %>% 
  filter(Medium.Type=="Control -"& Check.time==97)%>% 
  mutate(Medium.Type = ifelse(Medium.Type == "Test", "Insecticide medium", Medium.Type))%>% 
  mutate(PC.Direction = ifelse(Individual == "1", "No growth", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(Individual == "4", "No growth", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(Individual == "5", "No growth", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(Individual == "6", "No growth", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "no choice", "No choice", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "non chemical", "Without insecticide", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "right", "Right", PC.Direction)) %>% 
  mutate(PC.Direction = ifelse(PC.Direction == "left", "Left", PC.Direction))

```

#Dataframe creation for Path Chosen Barplots
```{r, echo=FALSE}
##TEST GROUP PATH CHOSEN

bar_PC_test_1<-data.frame(c("2Insecticide","1Without insecticide","3No choice","4No growth"),c(0,2,1,3))
colnames(bar_PC_test_1)<-c("PC.Direction","Number")
bar_PC_test_1

bar_PC_test_2<-data.frame(c("2Insecticide","1Without insecticide","3No choice","4No growth"),c(0,2,1,3))
colnames(bar_PC_test_2)<-c("PC.Direction","Number")
bar_PC_test_2

bar_PC_test_3<-data.frame(c("2Insecticide","1Without insecticide","3No choice","4No growth"),c(0,5,1,0))
colnames(bar_PC_test_3)<-c("PC.Direction","Number")
bar_PC_test_3

bar_PC_test_4<-data.frame(c("2Insecticide","1Without insecticide","3No choice","4No growth"),c(0,6,0,0))
colnames(bar_PC_test_4)<-c("PC.Direction","Number")
bar_PC_test_4


##POSITIVE CONTROL PATH CHOSEN

bar_PC_controlpos_1<-data.frame(c("1Left","2Right","3No choice","4No growth"),c(1,3,1,1))
colnames(bar_PC_controlpos_1)<-c("PC.Direction","Number")
bar_PC_controlpos_1

bar_PC_controlpos_2<-data.frame(c("1Left","2Right","3No choice","4No growth"),c(2,3,1,0))
colnames(bar_PC_controlpos_2)<-c("PC.Direction","Number")
bar_PC_controlpos_2

bar_PC_controlpos_3<-data.frame(c("1Left","2Right","3No choice","4No growth"),c(2,3,1,0))
colnames(bar_PC_controlpos_3)<-c("PC.Direction","Number")
bar_PC_controlpos_3

bar_PC_controlpos_4<-data.frame(c("1Left","2Right","3No choice","4No growth"),c(1,1,4,0))
colnames(bar_PC_controlpos_4)<-c("PC.Direction","Number")
bar_PC_controlpos_4



##NEGATIVE CONTROL PATH CHOSEN

bar_PC_controlneg_1<-data.frame(c("1Left","2Right","3No choice","4No growth"),c(0,0,1,5))
colnames(bar_PC_controlneg_1)<-c("PC.Direction","Number")
bar_PC_controlneg_1

bar_PC_controlneg_2<-data.frame(c("1Left","2Right","3No choice","4No growth"),c(2,0,3,1))
colnames(bar_PC_controlneg_2)<-c("PC.Direction","Number")
bar_PC_controlneg_2

bar_PC_controlneg_3<-data.frame(c("1Left","2Right","3No choice","4No growth"),c(2,2,1,1))
colnames(bar_PC_controlneg_3)<-c("PC.Direction","Number")
bar_PC_controlneg_3

bar_PC_controlneg_4<-data.frame(c("1Left","2Right","3No choice","4No growth"),c(1,0,1,4))
colnames(bar_PC_controlneg_4)<-c("PC.Direction","Number")
bar_PC_controlneg_4


```

#Data Representation

##Growth rate representation

```{r, echo=FALSE}
growth.medium9<-ggplot(GR_9, aes(x=Medium.Type, y=Growth, fill = Medium.Type)) +
  geom_boxplot()+theme_minimal() +
  xlab("Medium Type")+
  ylab("Growth rate (cm/h)")+
  theme(legend.position = "none")+
  scale_x_discrete(label=c("Control +","Chemical medium"))+
  scale_fill_brewer(palette="Greens")+
  scale_y_continuous(limits=c(0,0.3))


growth.medium49<-ggplot(GR_49, aes(x=Medium.Type, y=Growth, fill = Medium.Type)) +
  geom_boxplot()+theme_minimal()+
  xlab("Medium Type")+
  ylab(" ")+
  theme(legend.position = "none")+
  scale_x_discrete(label=c("Control +","Chemical medium"))+
  scale_fill_brewer(palette="Greens")+
  scale_y_continuous(limits=c(0,0.3))


plot_grid(growth.medium9,growth.medium49, labels=c("A","B"), ncol = 2, nrow = 1)


growth.check.control<-ggplot(GR_control, aes(x=Check.time, y=Growth, fill = Check.time)) +
  geom_boxplot()+theme_minimal()+
  xlab("Time passed since sampling")+
  ylab("Growth rate (cm/h)")+
  theme(legend.position = "none")+

  scale_fill_brewer(palette="Greens")+
  scale_y_continuous(limits=c(0,0.3))+
  scale_x_discrete(label=c("9h","49h"))

growth.check.insecticide<-ggplot(GR_insecticide, aes(x=Check.time, y=Growth, fill = Check.time)) +
  geom_boxplot()+theme_minimal()+
  xlab("Time passed since sampling")+
  ylab(" ")+
  theme(legend.position = "none")+
  scale_fill_brewer(palette="Greens")+
  scale_x_discrete(label=c("9h","49h"))+

  scale_y_continuous(limits=c(0,0.3))


plot_grid(growth.check.control,growth.check.insecticide, labels=c("A","B"), ncol = 2, nrow = 1)

m_insecticide_9<- GR_9 %>% 
  filter(Medium.Type=="Insecticide medium")
m_control_9<- GR_9 %>% 
  filter(Medium.Type=="Control +")

m_insecticide_49<- GR_49 %>% 
  filter(Medium.Type=="Insecticide medium")

m_control_49<- GR_49 %>% 
  filter(Medium.Type=="Control +")

mean(m_insecticide_9$Growth)
mean(m_insecticide_49$Growth)
mean(m_control_9$Growth)
mean(m_control_49$Growth)
```


##Path chosen representation
```{r, echo=TRUE}
pc_test_check1<-ggplot(data=bar_PC_test_1,aes(x=PC.Direction,y=Number,fill=PC.Direction))+
                  geom_bar(stat="identity",position=position_dodge(),color="black")+
  xlab(" ")+
  ylab("Number of individuals")+
  theme_minimal()+
  theme(legend.position = "none")+
  scale_x_discrete(labels = c('Non-chemical','Chemical', 'No choice', 'No growth'))+
  scale_y_continuous(limits=c(0,6))+
  scale_fill_brewer(palette="Greens")




pc_test_check2<-ggplot(data=bar_PC_test_2,aes(x=PC.Direction,y=Number,fill=PC.Direction))+
                  geom_bar(stat="identity",position=position_dodge(),color="black")+
  xlab(" ")+
  ylab(" ")+
  theme_minimal()+
  theme(legend.position = "none")+
  scale_x_discrete(labels = c('Non-chemical','Chemical', 'No choice', 'No growth'))+
  scale_fill_brewer(palette="Greens")+
  scale_y_continuous(limits=c(0,6))



pc_test_check3<-ggplot(data=bar_PC_test_3,aes(x=PC.Direction,y=Number,fill=PC.Direction))+
                  geom_bar(stat="identity",position=position_dodge(),color="black")+
  xlab(" ")+
  ylab("Number of individuals")+
  theme_minimal()+
  theme(legend.position = "none")+
  scale_x_discrete(labels = c('Non-chemical','Chemical', 'No choice', 'No growth'))+
  scale_fill_brewer(palette="Greens")+
  scale_y_continuous(limits=c(0,6))




pc_test_check4<-ggplot(data=bar_PC_test_4,aes(x=PC.Direction,y=Number,fill=PC.Direction))+
                  geom_bar(stat="identity",position=position_dodge(),color="black")+
  xlab(" ")+
  ylab(" ")+
  theme_minimal()+
  theme(legend.position = "none")+
  scale_x_discrete(labels = c('Non-chemical','Chemical', 'No choice', 'No growth'))+
  scale_fill_brewer(palette="Greens")+
  scale_y_continuous(limits=c(0,6))





##POSITIVE CONTROL 
pc_controlpos_check1<-ggplot(data=bar_PC_controlpos_1,aes(x=PC.Direction,y=Number,fill=PC.Direction))+
                  geom_bar(stat="identity",position=position_dodge(),color="black")+
  xlab(" ")+
  ylab("Number of individuals")+
  theme_minimal()+
  theme(legend.position = "none")+
  scale_x_discrete(labels = c("Left","Right","No choice","No growth"))+
  scale_fill_brewer(palette="Greens")+
  scale_y_continuous(limits=c(0,6))



pc_controlpos_check2<-ggplot(data=bar_PC_controlpos_2,aes(x=PC.Direction,y=Number,fill=PC.Direction))+
                  geom_bar(stat="identity",position=position_dodge(),color="black")+
  xlab(" ")+
  ylab(" ")+
  theme_minimal()+
  theme(legend.position = "none")+
  scale_x_discrete(labels = c("Left","Right","No choice","No growth"))+
  scale_fill_brewer(palette="Greens")+
  scale_y_continuous(limits=c(0,6))




pc_controlpos_check3<-ggplot(data=bar_PC_controlpos_3,aes(x=PC.Direction,y=Number,fill=PC.Direction))+
                  geom_bar(stat="identity",position=position_dodge(),color="black")+
  xlab(" ")+
  ylab("Number of individuals")+
  theme_minimal()+
  theme(legend.position = "none")+
  scale_x_discrete(labels = c("Left","Right","No choice","No growth"))+
  scale_fill_brewer(palette="Greens")+
  scale_y_continuous(limits=c(0,6))





pc_controlpos_check4<-ggplot(data=bar_PC_controlpos_4,aes(x=PC.Direction,y=Number,fill=PC.Direction))+
                  geom_bar(stat="identity",position=position_dodge(),color="black")+
  xlab(" ")+
  ylab(" ")+
  theme_minimal()+
  theme(legend.position = "none")+
  scale_x_discrete(labels = c("Left","Right","No choice","No growth"))+
  scale_fill_brewer(palette="Greens")+
  scale_y_continuous(limits=c(0,6))





##NEGATIVE CONTROL

pc_controlneg_check1<-ggplot(data=bar_PC_controlneg_1,aes(x=PC.Direction,y=Number,fill=PC.Direction))+
                  geom_bar(stat="identity",position=position_dodge(),color="black")+
  xlab(" ")+
  ylab("Number of individuals")+
  theme_minimal()+
  theme(legend.position = "none")+
  scale_x_discrete(labels = c("Left","Right","No choice","No growth"))+
  scale_fill_brewer(palette="Greens")+
  scale_y_continuous(limits=c(0,6))



pc_controlneg_check2<-ggplot(data=bar_PC_controlneg_2,aes(x=PC.Direction,y=Number,fill=PC.Direction))+
                  geom_bar(stat="identity",position=position_dodge(),color="black")+
  xlab(" ")+
  ylab(" ")+
  theme_minimal()+
  theme(legend.position = "none")+
  scale_x_discrete(labels = c("Left","Right","No choice","No growth"))+
  scale_fill_brewer(palette="Greens")+
  scale_y_continuous(limits=c(0,6))



pc_controlneg_check3<-ggplot(data=bar_PC_controlneg_3,aes(x=PC.Direction,y=Number,fill=PC.Direction))+
                  geom_bar(stat="identity",position=position_dodge(),color="black")+
  xlab(" ")+
  ylab("Number of individuals")+
  theme_minimal()+
  theme(legend.position = "none")+
  scale_x_discrete(labels = c("Left","Right","No choice","No growth"))+
  scale_fill_brewer(palette="Greens")+
  scale_y_continuous(limits=c(0,6))

pc_controlneg_check3


pc_controlneg_check4<-ggplot(data=bar_PC_controlneg_4,aes(x=PC.Direction,y=Number,fill=PC.Direction))+
                  geom_bar(stat="identity",position=position_dodge(),color="black")+
  xlab(" ")+
  ylab(" ")+
  theme_minimal()+
  theme(legend.position = "none")+
  scale_x_discrete(labels = c("Left","Right","No choice","No growth"))+
  scale_fill_brewer(palette="Greens")+
  scale_y_continuous(limits=c(0,6))


plot_grid(pc_test_check1,pc_test_check2,pc_test_check3,pc_test_check4,labels=c("A","B","C","D"), ncol = 2, nrow = 2)#TEST

plot_grid(pc_controlpos_check1,pc_controlpos_check2,pc_controlpos_check3,pc_controlpos_check4,labels=c("A","B","C","D"), ncol = 2, nrow = 2)#controlpos

plot_grid(pc_controlneg_check1,pc_controlneg_check2,pc_controlneg_check3,pc_controlneg_check4,labels=c("A","B","C","D"), ncol = 2, nrow = 2)#controlneg


```


#Tables creation for the tests of Path Chosen
```{r, echo=FALSE}
##TEST GROUP PATH CHOSEN

khi_PC_test_1 <- cbind(c(0,2,1,3))
dimnames(khi_PC_test_1)<-list((c("Without insecticide","Insecticide","No choice","No growth")))

khi_PC_test_1

khi_PC_test_2 <- cbind(c(0,2,1,3))
dimnames(khi_PC_test_2)<-list((c("Without insecticide","Insecticide","No choice","No growth")))

khi_PC_test_2

khi_PC_test_3 <- cbind(c(0,5,1,0))
dimnames(khi_PC_test_3)<-list((c("Without insecticide","Insecticide","No choice","No growth")))

khi_PC_test_3

khi_PC_test_4 <- cbind(c(0,6,0,0))
dimnames(khi_PC_test_4)<-list((c("Without insecticide","Insecticide","No choice","No growth")))

khi_PC_test_4

khi_PC_test<- head(cbind(khi_PC_test_1,khi_PC_test_2,khi_PC_test_3,khi_PC_test_4))


##POSITIVE CONTROL PATH CHOSEN

khi_PC_controlpos_1 <- cbind(c(1,3,1,1))
dimnames(khi_PC_controlpos_1)<-list((c("Left","Right","No choice","No growth")))


khi_PC_controlpos_1

khi_PC_controlpos_2 <- cbind(c(2,3,1,0))
dimnames(khi_PC_controlpos_2)<-list((c("Left","Right","No choice","No growth")))

khi_PC_controlpos_2

khi_PC_controlpos_3 <- cbind(c(2,3,1,0))
dimnames(khi_PC_controlpos_3)<-list((c("Left","Right","No choice","No growth")))

khi_PC_controlpos_3

khi_PC_controlpos_4 <- cbind(c(1,1,4,0))
dimnames(khi_PC_controlpos_4)<-list((c("Left","Right","No choice","No growth")))

khi_PC_controlpos_4

khi_PC_controlpos<- head(cbind(khi_PC_controlpos_1,khi_PC_controlpos_2,khi_PC_controlpos_3,khi_PC_controlpos_4))


##NEGATIVE CONTROL PATH CHOSEN

khi_PC_controlneg_1 <- cbind(c(0,0,1,5))
dimnames(khi_PC_controlneg_1)<-list((c("Left","Right","No choice","No growth")))

khi_PC_controlneg_1

khi_PC_controlneg_2 <- cbind(c(2,0,3,1))
dimnames(khi_PC_controlneg_2)<-list((c("Left","Right","No choice","No growth")))

khi_PC_controlneg_2

khi_PC_controlneg_3 <- cbind(c(2,2,1,1))
dimnames(khi_PC_controlneg_3)<-list((c("Left","Right","No choice","No growth")))

khi_PC_controlneg_3

khi_PC_controlneg_4 <- cbind(c(1,0,1,4))
dimnames(khi_PC_controlneg_4)<-list((c("Left","Right","No choice","No growth")))

khi_PC_controlneg_4

khi_PC_controlneg<- head(cbind(khi_PC_controlneg_1,khi_PC_controlneg_2,khi_PC_controlneg_3,khi_PC_controlneg_4))


```

#Statistical test

##Growth rate
##Is the growth rate negatively impacted by the presence of the insecticde ?

##Between test and control ?
#9h
```{r, echo=TRUE}
x <- GR[GR[,"Check.time"]==9 & GR[,"Medium.Type"]=="Test", "Growth"]
y <- GR[GR[,"Check.time"]==9 & GR[,"Medium.Type"]=="Control +", "Growth"]

var.test(x,y) #Variances inégales

shapiro.test(x)#Pas de normalité
shapiro.test(y)#p value = 0.0551


wilcox.test(x,y) #p value = 0.04225

```

#49h
```{r, echo=TRUE}
x <- GR[GR[,"Check.time"]==49 & GR[,"Medium.Type"]=="Test", "Growth"]
y <- GR[GR[,"Check.time"]==49 & GR[,"Medium.Type"]=="Control +", "Growth"]

var.test(x,y) #p value = 0.0006

shapiro.test(x)#p value = 0.004
shapiro.test(y)#p value = 0.1583

wilcox.test(x,y) #p value = 0.01768 w=3

```

##Between 9h and 49h ?
#Test group
```{r, echo=TRUE}
x <- GR[GR[,"Check.time"]==9 & GR[,"Medium.Type"]=="Test", "Growth"]
y <- GR[GR[,"Check.time"]==49 & GR[,"Medium.Type"]=="Test", "Growth"]

var.test(x,y) #p value = 0.02185

shapiro.test(x)#p value = 0.0006206
shapiro.test(y)#p value = 0.004039

wilcox.test(x,y) #p value = 0.6525 W=15

```

#Control group
```{r, echo=TRUE}
x <- GR[GR[,"Check.time"]==9 & GR[,"Medium.Type"]=="Control +", "Growth"]
y <- GR[GR[,"Check.time"]==49 & GR[,"Medium.Type"]=="Control +", "Growth"]

var.test(x,y) #p value = 0.1438

shapiro.test(x)#p value = 0.0551
shapiro.test(y)#p value = 0.1583

t.test(x,y, alternative = "two.sided", conf.level=0.95, paired = TRUE) #p value = 0.5411
d=0.0025/4

library(pwr)
pwr.t.test(d=d,n=6,sig.level=0.05,type="paired",alternative="two.sided")

```

##Path chosen
##Is the Physarum polycephalum capable to detect the presence of the insecticide and can it avoid it ?


#Test_check_1 (4h)
```{r, echo=FALSE}
chisq.test(khi_PC_test[,1])

```

#Test_check_2 (9h)
```{r, echo=FALSE}
chisq.test(khi_PC_test[,2])

```

#Test_check_3 (24h)
```{r, echo=FALSE}
chisq.test(khi_PC_test[,3])

```

#Test_check_4 (97h)
```{r, echo=FALSE}
chisq.test(khi_PC_test[,4])


```

#Control+_check_1 (4h)
```{r, echo=FALSE}
chisq.test(khi_PC_controlpos[,1])

```

#Control+_check_2 (9h)
```{r, echo=FALSE}
chisq.test(khi_PC_controlpos[,2])

```

#Control+_check_3 (24h)
```{r, echo=FALSE}
chisq.test(khi_PC_controlpos[,3])

```

#Control+_check_4 (97h)
```{r, echo=FALSE}
chisq.test(khi_PC_controlpos[,4])

```


#Control-_check_1 (4h)
```{r, echo=FALSE}
chisq.test(khi_PC_controlneg[,1])

```

#Control-_check_2 (9h)
```{r, echo=FALSE}
chisq.test(khi_PC_controlneg[,2])

```

#Control-_check_3 (24h)
```{r, echo=FALSE}
chisq.test(khi_PC_controlneg[,3])

```

#Control-_check_4 (97h)
```{r, echo=FALSE}
chisq.test(khi_PC_controlneg[,4])

```